Measuring contrast processing in the visual system using SSVEP

### 2024-05-06 review.qmd
ALmost done!

# Conclusions
The SSVEP is a powerful tool for studying contrast processing. It provides a high SNR readout of neuronal activity that is unambigously linked to the input. It is sensitive to both the amplitude and phase of the input and when combined with source imaging, it can be extracted from different cortical regions allowing researchers to track contrast processing computations across the visual pathway. Because of the high SNR, it can be measured in subjects where long recording durations are impractical (for example, infants) and at frequencies high enough to be effectively invisible [REF - Some high frequency work... - Romanian group]. The SSVEP is also able 'fingerprint' modulators of the input frequency through the harmonic and intermodulation terms they generate in the output. In principle, each nonlinearity in the visual pathway can be identified by

>>>>

# Future directions
The SSVEP is a powerful tool for studying contrast processing. It provides a high SNR readout of neuronal activity that is unambigously linked to the input. It is sensitive to both the amplitude and phase of the input and when combined with source imaging, it can be extracted from different cortical regions allowing researchers to track contrast processing computations across the visual pathway. Because of the high SNR, it can be measured in subjects where long recording durations are impractical (for example, infants or patients with neurological disorders) and at frequencies high enough to be effectively invisible [REF - Some high frequency work... - Romanian group]. The SSVEP is also able to 'fingerprint' modulators of the inputs through the harmonic and intermodulation terms they generate in the output. In principle, each nonlinearity in the visual pathway can be identified by its contribution to the frequency spectrum at different recording locations. This, it turn, allows researchers to study how contrast processing depends on spatial and temporal context and as well as changes in task, cognitive and behavioural state and arousal.

Although visual neuroscience is a relatively old field, there are still outstanding questions relating to contrast processing that could be addressed by SSVEP methods. For example, it is still not completely clear how contrast signals are computed in the human retina: although we have more than a century of electrophysiological data from animals, and the broad structure of cone inputs to retinal ganglion cells is understood [@LiFieldNeuron2014] we are still discovering new aspects of retinal processing that could influence the 'coining' of the visual system's currency [@gollischMeister2010, @WangPuthussery2023Nature, @uprety2022melanopsin]. The ability to frequency tag both inputs (for example, cone-directed luminance contrast) and modulators (for example, stimuli that selectively drive the intrinsically-photosensitive retinal ganglion cells) is a powerful tool to explore this first stage of image generation.

Later in the visual pathway, we would like to know more about the role of corticothalamic feedback in the LGN. Although it is commonly thought of as a simple relay between the eye and the cortex,  the majority of inputs to the LGN come from cortex not the eye, and there is good evidence that contrast processing in the LGN can be altered by top-down signals including attention [@BriggsUsrey2007, @ShermanGuillery1996, @OconnorNatNeuro2002, @GouwsJNS2014]. Bottom-up inputs to the LGN are segregated by eye and so responses there are often considered to be purely monocular but it is possible that feedback signals allow some binocular computations such as interocular normalisation [@ManyBakerRefs and others] to begin even at this relatively early stage. Frequency tagging inputs to different eyes or in different precortical pathways allows us to address neurons in different parts of the LGN. These techniques combined with advances in recording technology (for example, sensitive source-imaged EEG and MEG recordings that can resolve subcortical structures [@Attal2012, @AttalPlos12013, @Tesche1996], noninvasive deep-brain stimulation techniques [@MohammadjavadietalSciRep2022] or implanted electrode arrays [@KrolakSalmon2003]) may allow us to study these computations in more detail.

Finally...

(Adaptation, Amblyopia, Neurological disease, Chromatic channels and combinations, joint tuning for color/spatiotemporal frequncy/eye), contributions to gain pools (e.g. Solomon and Lennie 2006), inheritance of freqeuncy tags in higher areas, combination of low-level contrast features to make complex stimuli...)
